Loss recovery and tail loss performance in Multipath TCP

### 2017-01-07 main.tex
Update

Initial testing with customized program to send bursts of packets with fixed burst seperation. Adjust the burst seperation to get the desired scenario.

>>>>

Initial testing with customized program to send bursts of packets with fixed burst seperation. Adjust the burst seperation to get the desired scenario.
Results comparing the MPTCP-TLP for the considered cases are provided in figures~\ref{1pn},~\ref{2pn} and ~\ref{1ppn}. The improvement in latency
performance is seen Single packet tail loss with probe loss scenario. Single packet loss and Two packet loss scenarios provide increase in latency.
Analysis required in these two cases.

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.46\textwidth, natwidth=578.16,natheight=433.62]{plots/1PNew.pdf}
\caption{Single packet tail loss comparision with MPTCP-TLP}\label{1pn}
\end{center}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.46\textwidth, natwidth=578.16,natheight=433.62]{plots/2PNew.pdf}
\caption{Two packet tail loss comparison with MPTCP-TLP}\label{2pn}
\end{center}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.46\textwidth, natwidth=578.16,natheight=433.62]{plots/1PPNew.pdf}
\caption{Single packet tail loss together with probe loss with MPTCP-TLP}\label{1ppn}
\end{center}
\end{figure}
